\documentclass[a4paper,skipsamekey,11pt,english]{curve}

% Default biblatex style used for the publication list is IEEE with name sorting (use bibtex backend to avoid biber dependency).
\PassOptionsToPackage{backend=bibtex,style=ieee,sorting=ydnt,uniquename=init,defernumbers=true}{biblatex}

% Most commands and style definitions are in settings.sty.
\usepackage{settings}

% Load biblatex with the options passed above.
\usepackage{biblatex}

% Remove the default "[Online] Available:" prefix before URLs when using the IEEE style.
\DefineBibliographyStrings{english}{url={\textsc{url}}}

% Bibliography placeholder (not printed in this CV).
\addbibresource{own-bib.bib}

% Show photo only if wrapped in fullonly (currently unused).
\includecomment{fullonly}

\leftheader{%
  {\LARGE\bfseries\sffamily Juan Zaragoza Chichell}

  \makefield{\faEnvelope[regular]}{\href{mailto:jzaragoza@bcamath.org}{\texttt{jzaragoza@bcamath.org}}}
  \makefield{\faGithub}{\href{https://github.com/juanZaragozaChichell}{\texttt{juanZaragozaChichell}}}
  \makefield{\faLinkedin}{\href{https://www.linkedin.com/in/juan-zaragoza-chichell-421420203/}{\texttt{juan-zaragoza-chichell-421420203}}}
}

\rightheader{~}

\title{Curriculum Vitae}

\begin{document}
\makeheaders[c]

\makeatletter

% Education
\newcommand{\rubric@education}{%
  \section*{Education}
  \begin{itemize}
    \item \textbf{PhD in Computational Mathematics (Severo Ochoa Fellow)}\\
    BCAM - Basque Center for Applied Mathematics (Supervisor: Dr. Michael Bartoň)\\
    2022--present (final year)
    \item \textbf{MSc in Mathematical Research}\\
    Universitat Politècnica de València\\
    2022
    \item \textbf{BSc in Mathematics}\\
    Universidad de Salamanca\\
    2021
  \end{itemize}
}

% Research Stay
\newcommand{\rubric@researchstay}{%
  \section*{Research Stay}
  \begin{itemize}
    \item \textbf{Concordia University}\\
    Montreal, QC, Canada\\
    Sypervised by Dr. Tsz Ho Kwok; funded by MITACS Globalink Research Awards; focus on non-plannar 3D printing. To be published.\\
    Mar 15--Jun 15, 2025
  \end{itemize}
}

% Publications
\newcommand{\rubric@publications}{%
  \section*{Publications}
  \begin{itemize}
    \item \textbf{Evolution-based tool path and motion planning optimization for 5-axis CNC machining of free-form surfaces}\\
    J. Zaragoza Chichell, M. Bizzarri, J. Echevarrieta Ibarra, A. Pérez, M. Bartoň\\
    Computer-Aided Design, Vol. 190. 2025\\
    \item \textbf{On tool wear optimized motion planning for 5-axis CNC machining of free-form surfaces using toroidal cutting tools}\\
    K. Kruppa, J. Zaragoza Chichell, M. Bizzarri, M. Bartoň\\
    Computer-Aided Design, Vol. 189. 2025\\
    \item \textbf{Collision-free Tool Motion Planning for 5-Axis CNC Machining with Toroidal Cutters}\\
    J. Zaragoza Chichell, A. Rečková, M. Bizzarri, M. Bartoň\\
    Computer-Aided Design, Vol. 173. 2024\\
    
  \end{itemize}
}

% Talks
\newcommand{\rubric@talks}{%
  \section*{Talks \& Conferences}
  \begin{itemize}
    \item \textbf{Evolution-based tool path and motion planning optimization for 5-axis CNC machining of free-form surfaces}\\
    Symposium on Solid and Physical Modeling (SPM 2025), Hangzhou, Zhejiang, P.R. China.\\
    Oct 29--Nov 2, 2025
    \item \textbf{Collision-free Tool Motion Planning for 5-Axis CNC Machining with Toroidal Cutters}\\
    Symposium on Solid and Physical Modeling (SPM 2024), Concordia University, Montreal, QC, Canada. Best Paper Award (SPM 2024).\\
    Jul 8--10, 2024
    \item \textbf{An optimal and error free method for collision detection}\\
    Perspectivas de la investigación en matemáticas, Pamplona, Spain.\\
    Nov 15--16, 2023
  \end{itemize}
}

% Divulgation / Outreach
\newcommand{\rubric@divulgacion}{%
  \section*{Outreach}
  \begin{itemize}
    \item \textbf{Museum guide}\\
    Museo Universitario Didáctico e Interactivo de Ciencias (MUDIC), Orihuela, Spain.\\
    (University Didactic Interactive Science Museum)\\
    Developed and led interactive science communication activities for public audiences.\\
    2021
  \end{itemize}
}

\makeatother

\makerubric{education}
\makerubric{researchstay}
\makerubric{publications}
\makerubric{talks}
\makerubric{divulgacion}

\end{document}
